Ion pairing controls rheological properties of ``crocodile-line'' polyelectrolyte hydrogels

### 2016-02-01 PALSE/ion_pairing_paper.tex
cite Hyun2011 for maximum of loss modulus

Let us now discuss the rheological measurements and link them to the hydrogel microstructure. We reduce our measurements to two main observables, see Table~\ref{tab:results}: (i) the value of the shear modulus at small amplitude $G^\prime(\gamma\rightarrow 0)$, i.e. the elasticity of the undamaged gel network, and (ii) the critical strain $\gamma_c$ corresponding to the maximum of $G"$, that we consider as representative of the end of the linear regime and of the first broken cross-links. XXX Ref XXX

>>>>

Let us now discuss the rheological measurements and link them to the hydrogel microstructure. We reduce our measurements to two main observables, see Table~\ref{tab:results}: (i) the value of the shear modulus at small amplitude $G^\prime(\gamma\rightarrow 0)$, i.e. the elasticity of the undamaged gel network, and (ii) the critical strain $\gamma_c$ corresponding to the maximum of $G"$, that we consider as representative of the end of the linear regime and of the first broken cross-links\cite{Hyun2011}.
